From textual to structured Web API Descriptions {\large Knowledge Discovery and Data Mining Seminar 2017}

### 2017-08-30 Paper/Paper_KDD.tex
Algorithm updated
ALGO update
Update images
quellen K-Means, DBClustering eingefügt

% *** MATH PACKAGES ***
\usepackage{amsmath}
\usepackage{scrextend}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{color}
\usepackage{amssymb}
\usepackage{varwidth}
\usepackage{setspace}

@@

\subsection{Linked Web API Dataset}
Starting point was the Linked Web API dataset \cite{dojchinovskilinked} with 9.850 APIs. Besides short descriptions of the API, it inherits semantic annotations and links between different attributes like title, tags and links to websites. For our purpose only the descriptions were relevant. The first inspection showed, that the descriptions were too short. Since we want to cluster the APIs on similarity based on their descriptions, those were crucial. First solution was to crawl the website of the API to get more textual descriptions. This seemed to be easily done, since the dataset also had a link to the API documentation website. When checking the links, we found out that 78~\% (Fig. \ref{fig_sim2}) of the links were missing. From the remaining links only 9~\% were working. We tried to fix the rest of the links by deleting path and subdomain from the link. This slightly increased the amount of usable links. Overall the data quality which is achieved with this approach can be considered insufficient. A lot of the links do not point to the actual API description either because they are outdated or because the fixing approach just led us to a general page with often little connection to the API description.
\begin{figure}[h]
\centering
\includegraphics[width= 3.5in]{img/fig2.png}
\caption{Amount of working links in the Linked Web API Dataset}
\label{fig_sim2}
\end{figure}

\subsection{Programmable Web Dataset}
Another approach to get usable data was to crawl Programmable Web with over 15.800 APIs. Therefore, we constructed a crawler with the Scrapy Framework \footnote[2]{https://scrapy.org} to crawl all the data. The API descriptions from Programmable Web have an averege length of about 70 words, which we assumed to be not enough. We examined the links to the API documentation sites, to see if we can crawl them, too. From the 15.800 APIs, about 32~\% (Fig.  \ref{fig_sim3}) were not working. When we investigated the links deeper, we found out, that approximately 30 to 45~\% of the links redirect to a subpages like  main, authentication or payment pages. This was the same issue like with the Linked Web API dataset.
\begin{figure}[h]
\centering
\includegraphics[width= 2in]{img/pie.png}
\caption{Amount of working links in Programmable Web}
\label{fig_sim3}
\end{figure}

@@

\begin{algorithm}[H]
 \caption{Normalized Google Distance}
 \label{alg:algo1}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE word-vectors of the APIs
 \ENSURE  Correlation matrix
 \\ \textit{Procedure} :
\FOR {$\forall s_1 \in API$}
\FOR {$\forall s_2 \in API$} 
\STATE 
\parbox[c][1cm]{1\linewidth}{
$Sim_{con}(s_1,s_2)=$
}
\parbox[c][1cm]{1\linewidth}{
$\dfrac{\sum_{\epsilon\ {con}_{s1}}\sum_{w_j\epsilon\ {con}_{s2}}{1-NGD(w_i,\ w_j)}}{\left|{con}_{s1}\right|\times\left|{con}_{s2}\right|}$
}

 \STATE Add ${Sim}_{con}\left(s_1,s_2\right)$ to the correlation matrix 
\ENDFOR
\ENDFOR
\RETURN correlation matrix

% als inspiration ;)
 %\\ \textit{LOOP Process}
  %\FOR {$i = l-2$ to $0$}
  %\STATE statements..
  %\IF {($i \ne 0$)}
  %\STATE statement..
  %\ENDIF
  %\ENDFOR
 %\RETURN $P$
 \end{algorithmic}
 \end{algorithm}

@@

\subsection{Density-Based Clustering}
The first clustering algorithm we tried out was the density-based spatial clustering of applications with noise (DBSCAN). DBSCAN\cite{kanungo2002efficient} is a density based clustering algorithm grouping together closely packed data-points with a given number of neighbours required for a point to be dense ($minPts$) and a maximum distance between two neighbours in a cluster $(\epsilon)$ (Algorithm \ref{alg:algo2}).

\begin{algorithm}[H]
 \caption{Density-Based Clustering}
 \label{alg:algo2}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE given number of neighbours required for a point to be dense, \newline maximum distance between two
neighbours in a cluster, \newline word-vectors of the APIs
 \ENSURE  Clusters with associated APIs
 \\ \textit{Procedure}:
  \STATE Arbitrarily choose an initial API $s_1$
 \STATE

%...
% Das musst du irgendwie noch geschickter darstellen
 \end{algorithmic}
 \end{algorithm}

@@

\subsection{K-Means Clustering}
The clustering algorithm we used for our final implementation is K-Means, one of the most widely used clustering algorithm. For a given set of data-points in a n-dimensional space R\textsuperscript{n} and an integer $k$ the algorithm determines $k$ points, called centres, minimizing the sum of the mean square distance from the data points to their nearest centre. We are using the K-Means adaptation of the Lloyed-algorithm described in Algorithm \ref{Algorithm 3}\cite{kanungo2002efficient}.

@@

\begin{figure}[!t]
\centering
\includegraphics[width= 3.5in]{img/Jaccard.png}
\caption{Difference between Jaccard coefficient and F-messure}
\label{fig_sim4}
\end{figure}

>>>>

% *** MATH PACKAGES ***
\usepackage{amsmath}

\usepackage{scrextend}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{color}
\usepackage{amssymb}
\usepackage{varwidth}
\usepackage{setspace}

@@

\subsection{Linked Web API Dataset}
Starting point was the Linked Web API dataset \cite{dojchinovskilinked} with 9.850 APIs. Besides short descriptions of the API, it inherits semantic annotations and links between different attributes like title, tags and links to websites. For our purpose only the descriptions were relevant. The first inspection showed, that the descriptions were too short. Since we want to cluster the APIs on similarity based on their descriptions, those were crucial. First solution was to crawl the website of the API to get more textual descriptions. This seemed to be easily done, since the dataset also had a link to the API documentation website. When checking the links, we found out that 78~\% (Fig. \ref{fig_sim2}) of the links were missing. From the remaining links only 9~\% were working. We tried to fix the rest of the links by deleting path and subdomain from the link. This slightly increased the amount of usable links. Overall the data quality which is achieved with this approach can be considered insufficient. A lot of the links do not point to the actual API description either because they are outdated or because the fixing approach just led us to a general page with often little connection to the API description.
\begin{figure}[h]
\centering
\includegraphics[width= 3.5in]{img/graph2.pdf}
\caption{Amount of working links in the Linked Web API Dataset}
\label{fig_sim2}
\end{figure}

\subsection{Programmable Web Dataset}
Another approach to get usable data was to crawl Programmable Web with over 15.800 APIs. Therefore, we constructed a crawler with the Scrapy Framework \footnote[2]{https://scrapy.org} to crawl all the data. The API descriptions from Programmable Web have an averege length of about 70 words, which we assumed to be not enough. We examined the links to the API documentation sites, to see if we can crawl them, too. From the 15.800 APIs, about 32~\% (Fig.  \ref{fig_sim3}) were not working. When we investigated the links deeper, we found out, that approximately 30 to 45~\% of the links redirect to a subpages like  main, authentication or payment pages. This was the same issue like with the Linked Web API dataset.
\begin{figure}[h]
\centering
\includegraphics[width= 3.5in]{img/graph1.pdf}
\caption{Amount of working links in Programmable Web}
\label{fig_sim3}
\end{figure}

@@

\begin{algorithm}[H]
\caption{Normalized Google Distance}
\label{alg:algo1}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE word-vectors of the APIs
 \ENSURE  Correlation matrix
 \\ \textit{Procedure} :
\FOR {each API $s_1$}
\FOR {each API $s_2$} 
\STATE 
\parbox[c][1cm]{1\linewidth}{
$Sim_{con}(s_1,s_2)=$
}
\parbox[c][1cm]{1\linewidth}{
$\dfrac{\sum_{\epsilon\ {con}_{s1}}\sum_{w_j\epsilon\ {con}_{s2}}{1-NGD(w_i,\ w_j)}}{\left|{con}_{s1}\right|\times\left|{con}_{s2}\right|}$
}
 \STATE Add ${Sim}_{con}\left(s_1,s_2\right)$ to the correlation matrix 
\ENDFOR
\ENDFOR
\RETURN correlation matrix
 \end{algorithmic}
 \end{algorithm}

@@

\subsection{Density-Based Clustering}
The first clustering algorithm we tried out was the density-based spatial clustering of applications with noise (DBSCAN). DBSCAN\cite{dbscikit} is a density based clustering algorithm grouping together closely packed data-points with a given number of neighbours required for a point to be dense ($minPts$) and a maximum distance between two neighbours in a cluster $(\epsilon)$ (Algorithm \ref{alg:algo2}).

\begin{algorithm}[H]
\caption{Density-Based Clustering}
\label{alg:algo2}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE given number of neighbours required for a point to be dense, \newline maximum distance between two
neighbours in a cluster, \newline word-vectors of the APIs
 \ENSURE  Clusters with associated APIs
 \\ \textit{Procedure} :
  \FOR{each unvisited API S in dataset}
\STATE mark S as visited
\STATE N = getNeighbors(S)
\IF {sizeOf(N) $<$ minPts}
\STATE mark S as NOISE
\ELSE
\STATE C = next Cluster
\STATE expandCluster(S, N, C)
\ENDIF
\ENDFOR
\newline
 \end{algorithmic}
 \begin{algorithmic}[2]
 \STATE expandClusters(S, N, eps, minPts) :
\STATE add P to cluster C 
\FOR {each point in S'}
\IF {S' is not visited}
\STATE mark S' as visited
\STATE N' = getNeighbors(S')
\IF {sizeOf(N') $\geqslant$ minPts}
\STATE N = N joined with N'
\ENDIF
\ELSIF {P' is not yet menmer of any cluster}
\STATE add S' to cluster C
\ENDIF
\ENDFOR
 \end{algorithmic}
 \end{algorithm}

@@

\subsection{K-Means Clustering}
The clustering algorithm we used for our final implementation is K-Means, one of the most widely used clustering algorithm. For a given set of data-points in a n-dimensional space R\textsuperscript{n} and an integer $k$ the algorithm determines $k$ points, called centres, minimizing the sum of the mean square distance from the data points to their nearest centre. We are using the K-Means adaptation of the Lloyed-algorithm described in Algorithm \ref{Algorithm 3}\cite{nazeer2009improving}.

@@

\begin{figure}[!t]
\centering
\includegraphics[width= 3.5in]{img/eval.pdf}
\caption{Difference between Jaccard coefficient and F-messure}
\label{fig_sim4}
\end{figure}
